\chapter{Abstract}
The aim of this project is to develop a robust and enduring system using live data to analyze the correlation between a gamer's 
biometrics data and performance in a digital gaming scenario and corroborate the correlation by finding a function that approximates the relationship 
using machine learning algorithms.

Users' Biometric data were collected using a wearable device, Polar Vantage V2 and performance metrics were captured 
with a test game designed to test users' performance in a first-person shooter gaming scenario. Volunteers were selected and enrolled to gather biometric 
and test data. Heart Rate Variability, Heart Rate Average and Quality of Sleep were the biometric data collected and were used as the independent 
variables for the machine learning algorithm. The dependent variables to be predicted are the user's performance metrics in the test game. 
The performance metrics chosen were Fine Motor Average Tracking Time, Fine Motor Accuracy, Visual Average Response Time, Visual Average Tracking Time,
Visual Accuracy and Audio Average Response Time.

An on-cloud solution was proposed and implemented to access users' data and do real-time analysis. The solution was implemented using Amazon Web Services (AWS)
as the cloud provider, Amazon Relational Database Service (RDS) as a Platform as a Service (PaaS) provider and Amazon Elastic Compute Cloud (EC2) as an
Infrastructure as a Service (IaaS) provider.

Using an already predefined algorithm, a real-time model selection, hyperparameter tuning and model training pipeline were implemented to analyze the collected 
data. Various Machine Learning Models were developed and trained, enabling the team to make a strong case for correlation 
between biometric data and user performance in a digital gaming scenario. 
