\chapter{Conclusion}

The project was concluded successfully, and the team was able to deliver a working solution to the client's requirements. An enduring
solution capable of processing real-time data and on the fly was deployed to run a machine learning algorithm to predict user performance
based on their biometric data. Several challenges were encountered during the project because of limited resources available to the team
which meant discarding some industry-standard tools that could not work with the available resources. The chosen Virtual Machine (EC2 Micro)
has a capacity of 1GB RAM and 1 CPU, which was not enough to deploy an Angular Application and Docker. From the results of the analysis, the team
was able to show that there is a strong indication of correlation between the biometric data and the user performance. However, insufficient data
meant that the model could not be trained to a high degree of accuracy, and it is the opinion of the team that with more data, the model could only 
get better.


\subsubsection*{Otito}
This project was a great learning experience for me and an opportunity to work with various technologies. I was able to learn and understand how 
cloud-based web applications and services are developed and deployed. This project also gave me the opportunity to work with a client and understand 
the implications of changing requirements and how to adapt to them in a software development environment. I personally enjoyed working with the team and 
from a personal perspective, I strongly believe that the project was a success and it was down to everyone's hard work and dedication, and very proud of 
the work and ingenuity shown by the team in problem-solving. 

\subsubsection*{Rodrigo}

The journey through the project has been a challenging and rewarding experience. It gave me the opportunity to collaborate directly with a client and develop 
a solution that has real-world applications. I had the opportunity to work with technologies that were new to me, giving me the unique chance to expand my skill 
set, particularly in the areas of data analysis, machine learning, and cloud computing which is a field that we have not extensively covered in our course.  
This project brought to light the complexities involved in real-time data analysis and the design of robust system architectures. It reinforced the
importance of interdisciplinary knowledge and the integration of diverse technologies to address a complex real-world problem effectively. 
The collaboration between the team members was excellent, and we were able to combine our individual strengths to deliver a high-quality solution. 
The project was a valuable learning experience, and I am proud of the work we have accomplished.
